Using forecasting models for new book publishing

### 2015-08-10 paper.tex
arreglando un error de compilación-LaTeX

Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.

>>>>

Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/}} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.
